---
title: "R Notebook"
output: html_notebook
---

library(dplyr)
library(ggplot2)
library(urca)
library(TTR)
library(pastecs)

```{r}
ratings<-read.csv("ratings.csv")
movie_genres<-read.csv("movie_genres.csv")
ratings_genres<-ratings %>% select(movieId,rating,timestamp) %>% left_join( movie_genres %>% select(movieId,genres), by= c("movieId"="movieId"))
```

Calculate the age of movie when being rated (for a given movie, age:=timestamp-min(timestamp))

```{r}
movie_firsttime<-summarise(group_by(ratings_genres,movieId),firsttime=min(timestamp))
ratings_genres_age<-ratings_genres %>% left_join(movie_firsttime, by= c("movieId"="movieId"))
ratings_genres_age<-ratings_genres_age %>% mutate(age=timestamp-firsttime) %>% select(rating,genres,age)
```

```{r}
ratings_genres_cut<-ratings_genres_age
ratings_genres_cut$age<-cut(ratings_genres_cut$age,100)
ratings_genres_cut_group<-group_by(ratings_genres_cut,genres,age)
ratings_genres_age<-summarise(ratings_genres_cut_group,mean_rating=mean(rating))
```

Take Action movie for example

```{r}
rating_age_action<-subset(ratings_genres_age,genres=="Action")
rating_age_action<-ts(rating_age_action$mean_rating)
plot(rating_age_action)
```

Stationarity test (kpss)

```{r}
summary(ur.kpss(rating_age_action))
```

After testing stationarity, we can choose a 

Extract trend

```{r}
rating_age_action_trend<-SMA(rating_age_action)
plot.ts(rating_age_action_trend)
```

Test trend (There are no common methods for this test, I will figure out an interpretable if necessary)

```{r}
trend.test(rating_age_action, R=1)
```

Forecast









