---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
library(dplyr)
library(ggplot2)
library(urca)
library(TTR)
library(pastecs)
library(TSclust)
library(tidyr)
library(Hmisc)
```

Load data and add genres

```{r}
ratings<-read.csv("ratings.csv")
movie_genres<-read.csv("movie_genres.csv")
ratings_genres<-ratings %>% select(movieId,rating,timestamp) %>% left_join( movie_genres %>% select(movieId,genres), by= c("movieId"="movieId"))
```

Kruskal-Wallis H Test

```{r}
kruskal.test(rating~genres,data=ratings_genres)
```

Conclusion: p-value < 0.05, grouping by genres makes sense.

Calculate the age of movie when being rated (for a given movie, age:=timestamp-min(timestamp))

```{r}
movie_firsttime<-summarise(group_by(ratings_genres,movieId),firsttime=min(timestamp))
ratings_genres_age<-ratings_genres %>% left_join(movie_firsttime, by= c("movieId"="movieId"))
ratings_genres_age<-ratings_genres_age %>% mutate(age=timestamp-firsttime) %>% select(rating,genres,age)
```

Normalize the ratings based on genres (for all age together)

```{r}
ratings_genres_age_normalize_group<-group_by(ratings_genres_age,genres)
ratings_genres_age_normalize<-summarise(ratings_genres_age_normalize_group,rating_normalize=scale(rating),age=age)
```

Calculate the mean rating for each age based on genres (without normalization)

```{r}
ratings_genres_age_cut<-ratings_genres_age
ratings_genres_age_cut$age<-cut(ratings_genres_age_cut$age,100)
ratings_genres_age_cut_group<-group_by(ratings_genres_age_cut,genres,age)
ratings_genres_age_ts<-summarise(ratings_genres_age_cut_group,mean_rating=mean(rating))
ratings_genres_age_ts<-filter(ratings_genres_age_ts,genres!="(no genres listed)")
```

Calculate the mean rating for each age based on genres (with normalization)

```{r}
ratings_genres_age_normalize_cut<-ratings_genres_age_normalize
ratings_genres_age_normalize_cut$age<-cut(ratings_genres_age_normalize_cut$age,100)
ratings_genres_age_normalize_cut_group<-group_by(ratings_genres_age_normalize_cut,genres,age)
ratings_genres_age_normalize_ts<-summarise(ratings_genres_age_normalize_cut_group,mean_rating_normalize=mean(rating_normalize))
```


Take Action movie for example

Plot (without normalization)

```{r}
rating_age_ts_action<-subset(ratings_genres_age_ts,genres=="Action")
rating_age_ts_action<-ts(rating_age_ts_action$mean_rating)
plot(rating_age_ts_action)
```

Plot (with normalization)

```{r}
rating_age_normalize_ts_action<-subset(ratings_genres_age_normalize_ts,genres=="Action")
rating_age_normalize_ts_action<-ts(rating_age_normalize_ts_action$mean_rating_normalize)
plot(rating_age_normalize_ts_action)
```

Stationarity test (kpss)

```{r}
summary(ur.kpss(rating_age_ts_action))
```

After testing stationarity, we can choose a suitable model.

Extract trend

```{r}
rating_age_ts_trend_action<-SMA(rating_age_ts_action)
plot.ts(rating_age_ts_trend_action)
```

The trend for action movies is obviously upward.

Test trend

```{r}
trend.test(rating_age_ts_action, R=1)
```

Test trend for all genres

```{r}
rating_age_ts<-spread(ratings_genres_age_ts,genres,mean_rating)[,-1]
trend.p.value<-function(x){
  return(as.numeric(unlist(trend.test(x, R=1))[2]))
}
trend.rho<-function(x){
  return(as.numeric(unlist(trend.test(x, R=1))[3]))
}
genres_trend.p.value<-lapply(rating_age_ts,trend.p.value)
genres_trend.rho<-lapply(rating_age_ts,trend.rho)
```

Trend is not significant
```{r}
names(genres_trend.p.value[genres_trend.p.value>0.05])
```

Trend is not significant

Trend is upward
```{r}
names(genres_trend.p.value[(genres_trend.p.value<=0.05)&(genres_trend.rho>0)])
```

Trend is downward
```{r}
names(genres_trend.p.value[(genres_trend.p.value<=0.05)&(genres_trend.rho<=0)])
```

Plot trends for all genres
```{r}
ggplot(ratings_genres_age_ts, aes(x=age, y=mean_rating, colour=genres))+ 
  geom_point() +
  facet_grid(genres ~.)
```

Plot upward and significant trend
```{r}
plot(ts(rating_age_ts[,(genres_trend.p.value<=0.05)&(genres_trend.rho>0)]))
```

Plot downward and significant trend
```{r}
plot(ts(rating_age_ts[,(genres_trend.p.value<=0.05)&(genres_trend.rho<=0)]))
```

Plot upward and insignificant trend (Compared to the upward and significant one)
```{r}
plot(ts(rating_age_ts[,(genres_trend.p.value>0.05)&(genres_trend.rho>0)]))
```

Plot downward and insignificant trend (Compared to the downward and significant one)
```{r}
plot(ts(rating_age_ts[,(genres_trend.p.value>0.05)&(genres_trend.rho<=0)]))
```

Plot extracted upward and significant trend

```{r}
#impute missing data (use mean for each genre)
rating_age_ts<-mutate_all(rating_age_ts,impute,mean)
```

```{r}
plot(ts(mutate_all(rating_age_ts[,(genres_trend.p.value<=0.05)&(genres_trend.rho>0)],SMA)))
```

Plot extracted downward and significant trend
```{r}
plot(ts(mutate_all(rating_age_ts[,(genres_trend.p.value<=0.05)&(genres_trend.rho<=0)],SMA)))
```

For the siginificant trend, both upward and downward are obvious.

Plot extracted upward and not significant trend
```{r}
plot(ts(mutate_all(rating_age_ts[,(genres_trend.p.value>0.05)&(genres_trend.rho>0)],SMA)))
```

Plot extracted downward and not significant trend
```{r}
plot(ts(mutate_all(rating_age_ts[,(genres_trend.p.value>0.05)&(genres_trend.rho<=0)],SMA)))
```

We cannot extract obvious trend because they are not significant.

Clustering 
```{r}
Dist_rating_genres<-diss(rating_age_ts,"DTWARP")
heatmap(as.matrix(Dist_rating_genres))
Clust_genres<-hclust(Dist_rating_genres)
plot(Clust_genres)
```








